---
title: "EnerNOC Interview"
author: "Qiong Wu"
date: "March 18, 2015"
output: word_document
---
```{r echo = FALSE}
raw_data <- read.csv("Data2.csv")
indx <- dim(raw_data)[1]
names(raw_data) <- c("Date.Interval", "Reading")
date_data <- sapply(as.character(raw_data$Date.Interval), strsplit, split = " ")
dec_data <- data.frame(Date = vector("numeric", indx), Interval = vector("numeric", indx), Reading = vector("numeric", indx))
dec_data$Reading <- raw_data$Reading
for (i in 1:indx) {
       dec_data$Date[i] = date_data[[i]][1]
       dec_data$Interval[i] = date_data[[i]][2]
}
```

- There are **missing values** from the Raw Meter Reading

```{r echo = TRUE}
missing_reading <- dec_data[is.na(dec_data$Reading), ]
missing_reading
```

- This is a double check of number of **missing values** from Raw Meter Reading

```{r echo = TRUE}
missing_count <- sum(!complete.cases(dec_data))
missing_count
```

- There are **error readings** from Raw Meter Reading

```{r echo = TRUE}
error_reading <- dec_data[(dec_data$Reading < 0)&(!is.na(dec_data$Reading)), ]
error_reading
```

- This is a double check of number of **error readings** from Raw Meter Reading

```{r echo = TRUE}
error_count <- sum(dec_data$Reading < 0, na.rm = TRUE)
error_count
```

```{r echo = FALSE}
ave_data <- data.frame(day = vector("numeric", 31), ave.reading = vector("numeric", 31))
for (i in 1:31) {
png(paste0(i, "dec.png"))
date_index <- paste0("12/", paste0(i, "/07"))  
lab_dec_data <- dec_data[dec_data$Date == date_index, ]
ave_data$day[i] <- date_index
ave_data$ave.reading[i] <- mean(lab_dec_data$Reading[(lab_dec_data$Reading > 0) & !is.na(lab_dec_data$Reading)])     
plot(1:length(lab_dec_data$Interval), lab_dec_data$Reading, type = "l", col = "red", xlab = "5-min Interval", ylab = "Meter Reading", main = paste("Dec.", i, sep = " "))
dev.off()
}
```

```{r echo = FALSE}
ave_data$day <- strptime(ave_data$day, "%m/%d/%y")
```

- This is the table for **average reading for each day** basded on Raw Meter Reading

```{r echo = TRUE}
ave_data
```

- This is the point plot of average reading for each day of Dec. 2007

```{r echo = FALSE}
library(ggplot2)
qplot(day, ave.reading, data = ave_data, geom = "point", col = "red", xlab = "Day", ylab = "Average Reading (kWh)", main = "EnerNOC Meter Reading of Dec. 2007")
```

```{r echo = FALSE}
week_ave_data <- ave_data
week_ave_data$day <- weekdays(week_ave_data$day, abbreviate = T)
```

- This is the table of average reading for each day according to **weekdays**.

```{r echo = TRUE}
week_ave_data
```

- This is the point plot of average reading for each day according to **weekdays** of Dec. 2007 

```{r echo = FALSE}
qplot(day, ave.reading, data = week_ave_data, geom = "point", col = "red", xlab = "Week", ylab = "Average Reading (kWh)", main = "EnerNOC Meter Reading of Dec. 2007")
```
